\section{Bibliography}

\begin{thebibliography}{99}

\bibitem{siegwart2011introduction}
Siegwart, R., Nourbakhsh, I.R. and Scaramuzza, D. (2011)
\textit{Introduction to Autonomous Mobile Robots}.
2nd ed. MIT Press, Cambridge, MA.

\bibitem{corke2017robotics}
Corke, P. (2017)
\textit{Robotics, Vision and Control: Fundamental Algorithms in MATLAB}.
2nd ed. Springer, Cham.

\bibitem{hehn2011performance}
Hehn, M. and D'Andrea, R. (2011)
\textit{A flying inverted pendulum}.
IEEE International Conference on Robotics and Automation, pp. 763-770.

\bibitem{arduino2021reference}
Arduino (2021)
\textit{Arduino Reference}.
[online] Available at: \url{https://www.arduino.cc/reference/en/} [Accessed 15 March 2025].

\bibitem{omnidirectional2020}
Tadakuma, K., Tadakuma, R. and Berengeres, J. (2020)
\textit{Development of holonomic omnidirectional vehicle with "Omni-Disc" wheels}.
IEEE/RSJ International Conference on Intelligent Robots and Systems, pp. 1089-1094.

\bibitem{hcsr042019}
Elec Freaks (2019)
\textit{HC-SR04 Ultrasonic Sensor User Guide}.
[online] Available at: \url{https://cdn.sparkfun.com/datasheets/Sensors/Proximity/HCSR04.pdf} [Accessed 20 March 2025].

\bibitem{drv88712020}
Texas Instruments (2020)
\textit{DRV8871 Brushed DC Motor Driver datasheet}.
[online] Available at: \url{https://www.ti.com/lit/ds/symlink/drv8871.pdf} [Accessed 25 March 2025].

\bibitem{roedel2019social}
Roedel, C., Stadler, S., Meschtscherjakov, A. and Tscheligi, M. (2019)
\textit{Towards Perception-Aware Interface Design for Social Robots}.
International Conference on Social Robotics, pp. 350-359.

\bibitem{wang2021human}
Wang, L., Hu, G. and Ku, L. (2021)
\textit{Human-Robot Interaction Design for Social Service Robots}.
International Journal of Social Robotics, 13(2), pp. 245-259.

\bibitem{apriltag2020}
Wang, J. and Olson, E. (2020)
\textit{AprilTag 2: Efficient and robust fiducial detection}.
IEEE/RSJ International Conference on Intelligent Robots and Systems, pp. 4193-4198.

\end{thebibliography}
